Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Revising Lane's section
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1628 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

This paper describes the additions to the toolkit over the past year, which together form the 2.0 release. The software has been heavily used by the authors and several other groups in their daily research, and has been substantially refined since the first release.  The most important new functions in the toolkit are: 
\begin{itemize}
\item
Support for any style of synchronous context free grammar (SCFG)
% instead of just Hiero grammars.  This 
including syntax augment machine translation (SAMT) grammars \cite{samt2006},
\item
Support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Joshua-transliteration},  
\item
Lattice parsing for dealing with input uncertainty, including ambiguous output from speech recognizers or Chinese word segmenters  \cite{dyer-muresan-resnik:2008:ACLMain},
\item
Semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
Improvements to decoding through variational methods and approximations to intractable MAP decoding \cite{variational-decoding-acl09},
\item
Hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
Visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}, 
\item
A unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

Many research publications describe novel techniques and provide interesting results, yet fail to describe technical details in sufficient detail to allow their results to be reproduced by other researchers. Reproducibility in machine translation is made more challenging by the complexity of experimental workflows. Results in machine translation tasks are dependent on a cascade of processing steps and configurations.

\newcite{Schwartz-wmt10-pipline} describes a workflow framework for designing and running reproducible machine translation experiments using Joshua. Each step in the machine translation workflow (data preprocessing, grammar training, MERT, decoding, etc) is modeled by a GNU Make script which defines how to run the tools used in that step, and an auxiliary configuration file that defines the exact parameters to be used in that step during a particular run of an experiment. Workflows configured using this framework allow a complete experiment to be run - from downloading data and software through truecasing translated results - by executing a single make file.

This framework encourages researchers to supplement research publications with links to the complete set of scripts and configurations that were actually used to run the experiment. The scripts and configurations used to run the Johns Hopkins University submission to the 2010 WMT shared translation task are provided in \newcite{Schwartz-wmt10-pipline}.

\bibliographystyle{acl}
\bibliography{machinetranslation}

>>>>

This paper describes the additions to the toolkit over the past year, which together form the 2.0 release. The software has been heavily used by the authors and several other groups in their daily research, and has been substantially refined since the first release.  The most important new functions in the toolkit are: 
\begin{itemize}
\item
Support for any style of synchronous context free grammar (SCFG)
% instead of just Hiero grammars.  This 
including syntax augment machine translation (SAMT) grammars \cite{samt2006},
\item
Support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Joshua-transliteration},  
\item
Lattice parsing for dealing with input uncertainty, including ambiguous output from speech recognizers or Chinese word segmenters  \cite{dyer-muresan-resnik:2008:ACLMain},
\item
Semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
Improvements to decoding through variational methods and approximations to intractable MAP decoding \cite{variational-decoding-acl09},
\item
Hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
Visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}, 
\item
A convenient framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

Reproducing other researchers' machine translation experiments is difficult because the pipeline is too complex to fully detail in short conference papers. We have put together a workflow framework for designing and running reproducible machine translation experiments using Joshua \newcite{Schwartz-wmt10-pipline}. Each step in the machine translation workflow (data preprocessing, grammar training, MERT, decoding, etc) is modeled by a Make script that defines how to run the tools used in that step, and an auxiliary configuration file that defines the exact parameters to be used in that step for a particular experimental setup. Workflows configured using this framework allow a complete experiment to be run - from downloading data and software through scoring the final translated results - by executing a single Makefile.

This framework encourages researchers to supplement research publications with links to the complete set of scripts and configurations that were actually used to run the experiment. The Johns Hopkins University submission to the WMT10 shared translation task was implemented in this framework, and can be easily and exactly reproduced by other researchers by typing a single command. 
\bibliographystyle{acl}
\bibliography{machinetranslation}
